Staged Abstract Interpreters

### 2019-09-11 paper/50_stageabs.tex
typo

\paragraph{Partially-static Data}
Our treatment of binding-times is coarse-grained: @Expr@s is static, the rest
of the components are all dynamic. But this is not always true, because the
static data have to be used somewhere with the dynamic operations.
Partial-static data is a way to improve binding-times and optimize the
generated code.
For example, to fold a static singleton set (often appears in @SetT@), e.g.,
@Set(x).foldLeft(init)(f)@ where @x@ and @init@ are staged values, a naive code
generator would faithfully generates code that applies @foldLeft@ with the set
and function @f@. But we can also utilize algebraic properties of @foldLeft@
to generate cheaper code, e.g., @Set(x).foldLeft(init)(f) = f(init, x)@. Since the
function @f@ is known at the current stage, we completely eliminate the fold
operation and function application. We apply several rewritings enabled by
partial-static patterns, such as for @Set@, @Map@, and @Tuple@. This
optimizations greatly reduces the size of residual programs.

>>>>

\paragraph{Partially-static Data}
Our treatment of binding-times is coarse-grained: @Expr@s is static, the rest
of the components are all dynamic. But this is not always true, because the
static data have to be used somewhere with the dynamic operations.
Partial-static data is a way to improve binding-times and optimize the
generated code.
For example, to fold a static singleton set (often appears in @SetT@), e.g.,
@Set(x).foldLeft(init)(f)@ where @x@ and @init@ are staged values, a naive code
generator would faithfully generate code that applies @foldLeft@ with the set
and function @f@. But we can also utilize algebraic properties of @foldLeft@
to generate cheaper code, e.g., @Set(x).foldLeft(init)(f) = f(init, x)@. Since the
function @f@ is known at the current stage, we completely eliminate the fold
operation and function application. We apply several rewritings enabled by
partial-static patterns, such as for @Set@, @Map@, and @Tuple@. This
optimization greatly reduces the size of residual programs.
